Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-18 paper.tex
cite for social systems

One domain where these challenges are particularly evident is Cyber-Physical Swarms (CPSs, or \emph{swarm-like systems}), 
 where a large number of agents interact with each other and their environment based on spatial proximity. 
%
Examples of CPSs include swarm robotics, smart cities~\cite{bajovic2021marvel}, sensor networks~\cite{pianini2022collective}, and social systems. 
 In these systems, agents need to adapt to dynamic and uncertain situations, while ensuring the achievement of global objectives that may not be directly observable or measurable by individual agents.

>>>>

One domain where these challenges are particularly evident is Cyber-Physical Swarms (CPSs, or \emph{swarm-like systems}), 
 where a large number of agents interact with each other and their environment based on spatial proximity. 
%
Examples of CPSs include swarm robotics~\cite{brambilla2013swarm}, smart cities~\cite{bajovic2021marvel}, sensor networks~\cite{pianini2022collective}, and social systems~\cite{zhou2019cyber}. 
 In these systems, agents need to adapt to dynamic and uncertain situations, while ensuring the achievement of global objectives that may not be directly observable or measurable by individual agents.
